---
title: "STAT 308 Final Project"
author: "Kim Ting Li, Claire Guo"
date: "May 22, 2018"
output: pdf_document
---
```{r}
library("R.matlab")
Subject = readMat("./data-starplus-04847-v7.mat")
n = Subject$meta[[3]] # number of voxels = 4698
voxel_coords = Subject$meta[[1]] # n-by-3 matrix with voxel_coords[i,] = (x,y,z) coordinates of voxel #i
voxel_activity = list()

ROI_names = unlist(Subject$meta[[16]][1,,])[-4]
ROI_voxels = rep(0,n); for(i in 1:n){tmp = which(ROI_names == c(Subject$meta[[17]][[i]][[1]])); if(length(tmp)>0){ROI_voxels[i]=tmp}} # ROI_voxels[i] = 0 if voxel i is not assigned to any ROI

```

```{r}
n_ROI=length(ROI_names)
n_voxels_in_ROI=matrix(NA,2,n_ROI)
for (i in 1:n_ROI) {
  n_voxels_in_ROI[1,i]=i
  n_voxels_in_ROI[2,i]=sum(ROI_voxels==i)
}

n_voxels_in_ROI
```

```{r}
Sigma <- 
```







```{r}
group_adaptive_BH<-function(P,group_sizes,alpha,gamma,signal){
  a=length(group_sizes)
  pi<-c()
  p_til<-c()
  #split into groups of different sizes (vector n)
  g<-split(P, rep(seq_along(group_sizes), group_sizes)) 
  for (i in 1:a){
   pi[i]<-sum(g[[i]]>gamma)/(group_sizes[i]*(1-gamma)) 
  }
    for (i in 1:a){
    for (j in 1:group_sizes[i]){
        temp=g[[i]][j]*pi[i] 
        p_til=c(p_til,temp)  
        }#how to write a continuous p_til
      }
  for (i in 1:length(P)){
    if(p_til[i]>gamma){
      p_til[i]=Inf
    }
  }
  k = max(which(sort(p_til)<=(1:length(P))/length(P) * alpha))
  power=sum(p_til[which(signal==1)] <= alpha*k/length(P))/sum(signal)
  FDP=sum(signal[which(p_til <= alpha*k/length(P))]==0)/sum(p_til <= alpha*k/length(P))
  output=c(FDP,power)
  return(output)
}
```

##1b Below I generated data vector P containing 10 groups of nulls and 10 groups of 50% signals. Then I made a signal vector to indicate the position of signals for my group_adaptative_BH function. we then try when there are 20 groups with 50 data points each and got FDP=0.115 and power=0.644. We then tried it on a single group of 1000 and got FDP=0.097, and power=0.556. As we can see, with single group, we get less FDP but also less power. It is a more conservative approach then the one adjusted for groups.
```{r}
set.seed(123)
n<-rep(50,20)
alpha=0.1
gamma=0.5
rep=50
k<-c()
generate<-function(){
  second.ten=c()
  first.ten=runif(500,0,1)
  for (i in 1:10) {
    z=rnorm(25,2,1)
    sig=pnorm(-abs(z))
    second.ten=c(second.ten,runif(25,0,1),sig)
  }
   P=c(first.ten,second.ten) 
   return(P)
}
P<-generate()
signal=c(rep(0,500),rep(c(rep(0,25),rep(1,25)),10))
output=group_adaptive_BH(P,n,alpha,gamma,signal)
output
```
```{r}
output.onegroup=group_adaptive_BH(P,1000,alpha,gamma,signal)
output.onegroup
```

